Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-26 paper/galsize_paper.tex
Resolved mysterious latex compilation bug by commenting out use of latex geometry package - pushing new branch to avoid potential conflicts with possible changes already locally implemented by @a-kravtsov
Further changes to abstract

\documentclass[usenatbib,usegraphicx,letterpaper]{mn2e}
\usepackage[totalwidth=480pt,totalheight=680pt]{geometry}

@@

\begin{abstract}
Using new SDSS measurements of projected galaxy clustering, $\wproj(\rproj),$ we place empirical constraints on the connection between galaxy size, $\rhalf,$ and halo virial radius, $\rvir.$  
We find that small galaxies cluster much more strongly than large galaxies of the same stellar mass. 
The size-dependence of $\wproj(\rproj)$ increases on smaller scales, and decreases at larger stellar mass. Using {\tt Halotools} to forward model the observations, we show that a simple empirical model, in which galaxy $\rhalf$ is proportional to halo $\rvir$ at the time when halo mass reached its maximum,
reproduces the observed size-dependence of $\wproj(\rproj)$ in striking detail. 
We show that the success of this model provides strong support for the conclusion that satellite galaxies have smaller sizes relative to central galaxies of the same halo mass. 
Our findings indicate that the sizes of satellites are set prior to the time of satellite infall, and that a remarkably simple, linear size--virial radius relation emerges from the complex physics regulating galaxy size. 
%We conclude with a prediction that future measurements of galaxy-galaxy lensing will show that small galaxies exhibit a significantly stronger lensing signal relative to large galaxies.of the same stellar mass. 
\end{abstract}

>>>>

\documentclass[usenatbib,usegraphicx,letterpaper]{mn2e}
%\usepackage[totalwidth=480pt,totalheight=680pt]{geometry}

@@

\begin{abstract}
Using new SDSS measurements of projected galaxy clustering, $\wproj(\rproj),$ we place empirical constraints on the connection between galaxy size and halo virial radius.  
We find that small galaxies cluster much more strongly than large galaxies of the same stellar mass. 
The magnitude of this clustering difference increases on small scales, and decreases with stellar mass. Using {\tt Halotools} to forward model the observations, we test a simple empirical model in which present-day galaxy size is proportional to the size of the virial radius at the time the halo reached its maximum mass. This simple model reproduces the observed size-dependence of $\wproj(\rproj)$ in striking detail. 
The success of this model provides strong support for the conclusion that satellite galaxies have smaller sizes relative to central galaxies of the same halo mass. 
Our findings indicate that satellite size is set prior to the time of infall, and that a remarkably simple, linear size--virial radius relation emerges from the complex physics regulating galaxy size. 
We make quantitative predictions for future measurements of galaxy-galaxy lensing, including dependence upon size, scale, and stellar mass, and provide a simple scaling relation that can be used to calibrate hydrodynamical simulations and semi-analytic models. 
\end{abstract}
